On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-09-29 paper/paper.tex
Add some description of the C backend towards the beginning of the paper

@@

>>>>

In this paper, a C backend is given as an example. The Core plugin will
translate a subset of Haskell to the EDSL we have specified. The C backend will
then take expressions written in this EDSL and translate them to C code. This C
code can be compiled by a standard C compiler. In effect, the subset of Haskell
represented in the EDSL is compiled to C.

@@

A C backend is described in this paper. However, other backends could be constructed,
targeting different architectures.
